Towards typed repositories of proofs \\[0.6em] \small \textsf{MIPS 2010}

### 2010-07-06 talks/MIPS2010/slides.tex
2e slide corrigé
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@141 403e655e-980a-47bd-8c60-1ee5348bb6b7

\hrule
\begin{frame}{A paradoxical situation}  
  \begin{block}{Observation}
    Workflow of formal mathematics was largely inspired by software
    development:
    \begin{itemize}
    \item File-based scripts (\textsf{emacs})
    \item Separate compilation (\textsf{make})
    \item Text-based versioning (\textsf{svn}, \textsf{diff}s\ldots)
    \end{itemize}
  \end{block}
  \pause
  \begin{block}{Mission}
    \large \it Isn't it time to adapt these tools to proofs?
  \end{block}
  {\Large }
\end{frame}
\hrule

@@

The paradox about this situation is that these very tools can be used
to reason about formal languages and especially proof
languages: some of these tools are even dedicated to the formalization
of proof systems and their properties. But we still use the legacy
generic tools to manage our developments.

@@

In the following, I will present a preliminary implementation of these
ideas. It is a meta-language for incremental proof-checking, that is a
language in which one can define abstract syntaxes, logical rules and
proofs, and allows to check validity, and express the incrementality
of the constructions. It can be viewed as a kernel for a typed version
control system.

>>>>

\hrule
\begin{frame}{A paradoxical situation}  
  \begin{block}{Observation}
    Workflow of formal mathematics was largely inspired by software
    development:
    \begin{itemize}
    \item File-based scripts (\textsf{emacs})
    \item Separate compilation (\textsf{make})
    \item Text-based versioning (\textsf{svn}, \textsf{diff}s\ldots)
    \end{itemize}
  \end{block}
  \pause
  \begin{block}{\ldots\ And yet,}
    Powerful tools to mechanize the metatheory of (proof) languages
  \end{block}
  \vspace{0.6em}
  \pause
  \begin{center}
    {\large \it Isn't it time to make these tools metatheory-aware?}
  \end{center}
\end{frame}
\hrule

@@

The paradox about this situation is that these very tools can be used
to reason about formal languages and especially proof languages: some
of these tools are even dedicated to the mechanization of the
metatheory of proof languages. But we still use the legacy generic
tools to manage our developments.

@@

In the following, I will present a preliminary implementation of these
ideas. It is a meta-language for incremental proof-checking, that is a
language in which one can define abstract syntaxes, logical rules and
proofs, and allows to check validity, and express the incrementality
of the constructions. It can be viewed as a kernel for a generic,
typed version control system.
